\cvsection{Research \& Publications}
\begin{cventries}
  \cventry
    {}%this is for extra space 
    {Journal:}
    {} {}%this is for spacing 
    {
      \begin{cvitems}
      {
        \item {Shaikh Mohd. Laeeq, Gangadhar N. D.., Brian Gee Chacko     “Design and Development of an
            Efficient H.264 Video Encoder for CPU/GPU using OpenCL” SASTECH Journal, Volume 11,
            Issue 2, Sep 2012, Page no 30.}
      }
      \end{cvitems}
    }
  \cventry
    {}
    {Conferences:}
    {} {}%this is for spacing 
    {
      \begin{cvitems}
      {
        \item {Shaikh Mohd. Laeeq, Deepali Borade “Mechanism of Determining Page faults Instantaneously
        via Device Driver based Approach in Linux” IEEE SCEECS 2012, Conference Proceedings,
        Page no 566.}
        \item {Shaikh Mohd. Laeeq, Deepali Borade “Performance and Evaluation of IEEE 802.15.4 under
        Different Topologies with Ad-hoc On Demand Distance Vector Protocol” IEEE SCEECS 2012,
        Conference Proceedings, Page no 210.}
        \item {K. Sohel Rana, Mohammed Laeeq Shaikh, Sayyad Ajij D. , "Survey, Study and Review of
        Coordinate System Notations using 3D Environment for Better Understanding of EM Fields
        Behavior" by IEEE WCON 2016, Hyderabad, India.}
      }
      \end{cvitems}
    }
    {}%this is for spacing
    \cventry
    {}
    {Patents and IP:}
    {} {}%this is for spacing 
    {
        \begin{cvitems}
        {
            \item {Dr R. R. Deshmukh, Dr Pramod B. Patil, Kanchan S. Bhagat, Dr. Dnyaneshwar K. Kirange, Dr.
            Shubhangi D. Patil, Dr. Jitendra P. Chaudari, Mohammed Laeeq, " SOPES: Method, Apparatus,
            System, Protocol and Process of Self Organized Emergency Services" 201821037901, TEMP/E-
            1/41190/2018-MUM}
            %
            \item {Dr. R. R. Deshmukh, B. S. Sonawane, Mohammed Laeeq, Pushpendra Chavan, Dr. Aaron
            Mogeni Oirere, Pukhraj Shrishrimal, Swapnil D. Waghmare, "Method, Apparatus, and System for
            Virtualized, Diskless Computing System for Educational Applications and Research", Reference no. 201721019076, Application no. TEMP/E-1/19389/2017-MUM}
            %
            \item {Shaikh Mohammed Laeeq, "Method, system, and process of multi unmanned aerial vehicle information and state sharing",201721004935,TEMP/E-1/451/2017-MUM}
            %
            \item {Dr. R. R. Deshmukh, Shubhangi D Patil, Dr. D K Kirange, Mr K .S. Bhagat, Mohammed Laeeq, B. S. Sonawane, "SAAAD: Self adaptive apriori algorithm based embedded systems device", 201721042194, TEMP/E-1/42798/2017-MUM}
        }
        \end{cvitems}
    }

%this is for putting numbers before references 
%\setcitestyle{numbers}
%this is fo the detailed biblography style 
%\nocite{*}                          % cite everything
%\citep{Chacko2012}
%\citep{Laeeq2012}
%\citep{Borade2012}
%\citep{Rana2016}

%\printbibliography[heading = none,keyword = article,env = mybib]
% no heading (e.g., "References")
%keyword = article,                  % FILTER BY < article > KEYWORD
%env = mybib]                        % Use mybib style


%\bibliographystyle{unsrtnat}
%this is for the .bib file 
%\bibliography{my_papers_}	

\end{cventries}
 